mir\_eval

### 2014-05-04 paper/paper.tex

\def\eg{\emph{e.g.\/}}
\def\ie{\emph{i.e.\/}}
\def\etc{\emph{etc.\/}}
\def\etal{\emph{et al.\/}}
\DeclareMathOperator*{\median}{median}
\newcommand{\ind}[1]{\ensuremath{\left\llbracket#1\right\rrbracket}}
\def\given{\ensuremath{|~}}
\def\defeq{\ensuremath{:=}}

@@

\subsubsection{Boundary annotation}

Within boundary annotation, there are two categories of evaluation metrics: detection,
and deviation~\cite{turnbull2007supervised}.

\emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
a window, typically either $0.5$s or $3.0$s.  
A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
\leq W$.

No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
\begin{align}
P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
\end{align}
and the corresponding F-measure is defined by taking their harmonic mean.

\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
\begin{align}
\text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
\text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
\end{align}

\subsubsection{Structural annotation}
Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.

Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
reported in the reference annotation, and synthesizing unique labels if necessary.

Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
analogously for the estimation.  Precision and recall are defined as
\begin{align}
P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
\end{align}

\emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
\begin{align}
P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
\end{align}
Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
Lukashevich~\cite{lukashevich2008towards}.

The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
\begin{align}
S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
\end{align}
where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.

>>>>

\def\eg{\emph{e.g.}}
\def\ie{\emph{i.e.}}
\def\etc{\emph{etc.}}
\def\etal{\emph{et al.}}
\DeclareMathOperator*{\median}{median}
\newcommand{\ind}[1]{\ensuremath{\left\llbracket#1\right\rrbracket}}
\def\given{\ensuremath{|~}}
\def\defeq{\ensuremath{:=}}

\def\mireval{\texttt{mir\_eval}}

@@

\mireval implements the following MIREX-compatible boundary detection metrics:
\begin{description}
\item[Boundary detection:] precision, recall, and F-measure for detecting boundary
events within a tolerance window $w\in \{0.5, 3\}$~\cite{turnbull2007supervised};
\item[Boundary deviation:] median absolute time difference from a reference boundary
to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
\end{description}
and the following structure annotation metrics
\begin{description}
\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs
of sampled time instants as belonging to the same structural
component~\cite{levy2008structural};
\item[Rand index:\footnote{The MIREX results page refers to Rand index as ``random
clustering index''.}] reference and estimated annotations are sampled uniformly
throughout the track, and the induced clusterings are compared by the Rand index
~\cite{rand1971objective};
\item[Normalized conditional entropy:] reference and estimated labels are sampled
uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are
computed by estimating the conditional entropy of $Y_R$ given $Y_E$
(\emph{under-segmentation}) and $Y_E$ given $Y_R$ 
(\emph{over-segmentation})~\cite{lukashevich2008towards}.
\end{description}

% \subsubsection{Boundary annotation}

% Within boundary annotation, there are two categories of evaluation metrics: detection,
% and deviation~\cite{turnbull2007supervised}.

% \emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
% Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
% a window, typically either $0.5$s or $3.0$s.  
% A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
% \leq W$.

% No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
% This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
% using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
% implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
% \begin{align}
% P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
% R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
% \end{align}
% and the corresponding F-measure is defined by taking their harmonic mean.

% \emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
% These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
% alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
% \begin{align}
% \text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
% \text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
% \end{align}

% \subsubsection{Structural annotation}
% Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
% and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
% labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
% and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.

% Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
% This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
% reported in the reference annotation, and synthesizing unique labels if necessary.

% Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
% recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
% Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
% analogously for the estimation.  Precision and recall are defined as
% \begin{align}
% P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
% R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
% \end{align}

% \emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
% the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
% \begin{align}
% P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
% \end{align}
% Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
% The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
% empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
% Lukashevich~\cite{lukashevich2008towards}.

% The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
% \begin{align}
% S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
% S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
% \end{align}
% where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.
